### 2023-10-26 manuscript.tex
Changed order of panel captions

\begin{figure}[h!]
\includegraphics[width=\textwidth]{simulation/out/simulation.png}
\centering
\caption{\textbf{Hypothesis testing statistics under simulated BM and OU models.}
\textbf{(A)} Violin plots of the estimated rates as a function of the true rates ($\sigma^2_{BM}$) under the BM model. \textbf{(B)} The probability of incorrectly rejecting the BM model in favor of the OU model (type I error) as a function of a given critical value of the log likelihood ratio. Each line indicates a different value of the true rate under the BM model. \textbf{(C)} Type I error as a function of a given critical value as in panel B but with all simulations under different values of the true rate combined into a single data set. \textbf{(D)} $\log_{10}$ ratio of the mean estimated rate over its true value as a function of the true rates ($\sigma^2_{OU}$) and selection strengths ($\alpha$) \textbf{(E)} $\log_{10}$ ratio of the mean estimated selection strength over its true value as a function of the true rates ($\sigma^2_{OU}$) and selection strengths ($\alpha$) \textbf{(F)} The probability of incorrectly failing to reject the BM model in favor of the OU model (type II error) as a function of the true rates ($\sigma^2_{OU}$) and selection strengths ($\alpha$). The probabilities were calculated using the critical value obtained from the empirical 1\% type I error rate shown in panel C.}
\label{fig:simulation}
\end{figure}

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{simulation/out/simulation.png}
\centering
\caption{\textbf{Hypothesis testing statistics under simulated BM and OU models.}
\textbf{(A)} Violin plots of the estimated rates as a function of the true rates ($\sigma^2_{BM}$) under the BM model. \textbf{(B)} $\log_{10}$ ratio of the mean estimated rate over its true value as a function of the true rates ($\sigma^2_{OU}$) and selection strengths ($\alpha$). \textbf{(C)} $\log_{10}$ ratio of the mean estimated selection strength over its true value as a function of the true rates ($\sigma^2_{OU}$) and selection strengths ($\alpha$). \textbf{(D)} The probability of incorrectly rejecting the BM model in favor of the OU model (type I error) as a function of a given critical value of the log likelihood ratio. Each line indicates a different value of the true rate under the BM model. \textbf{(E)} Type I error as a function of a given critical value as in panel D but with all simulations under different values of the true rate combined into a single data set. \textbf{(F)} The probability of incorrectly failing to reject the BM model in favor of the OU model (type II error) as a function of the true rates ($\sigma^2_{OU}$) and selection strengths ($\alpha$). The probabilities were calculated using the critical value obtained from the empirical 1\% type I error rate shown in panel E.}
\label{fig:simulation}
\end{figure}
